readme

### 2024-07-16 README.Rmd
Prettify all the codes with the package styler

```{r}
#Uncomment the below two lines if you use the library for the first time of if
#you want to update the library
#install.packages("devtools")
#devtools::install_github("nasserdr/digiRhythm", dependencies = TRUE)
```
## Example

@@

#The file name with the path
url <- 'https://github.com/nasserdr/digiRhythm_sample_datasets/raw/main/516b_2.csv'
download.file(url, destfile = '516b_2.csv')
filename <- file.path(getwd(), '516b_2.csv')

#The columns that we are interested in
colstoread <- c("Date", "Time", "Motion Index", 'Steps')

#Reading the activity data from the csv file
data <- import_raw_icetag_data(filename = filename, skipLines = , act.cols.names = colstoread, sampling = 15)

print(head(data))

```

@@

```{r visualize, message=FALSE, warning=FALSE, paged.print=FALSE}
data("df691b_1", package = "digiRhythm")
df <- remove_activity_outliers(df691b_1)
df_act_info(df)
activity = names(df)[2]
start <- "2020-08-25"
end <- "2020-10-11"
save <- TRUE
outputdir <- 'testresults'
outplotname <- 'myplot'
width <- 10
device <- 'tiff'
height <-  5
actogram(df, activity, start, end, save = FALSE,
     outputdir = 'testresults', outplotname = 'actoplot', width = 10,
     height =  5, device = 'tiff')
```

@@

```{r dfc_example, results = FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- remove_activity_outliers(df516b_2)
df_act_info(df)
activity = names(df)[2]
my_dfc <- dfc(df, activity , sampling = 15, show_lsp_plot = FALSE)

#You may want to explore the two list inside my_dfc.
#DFC and SPECTRUM are saved inside my_dfc, each as a list
```

@@

```{r dindex_example, results = FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- remove_activity_outliers(df516b_2)
df_act_info(df)
activity = names(df)[2]
d_index <- diurnality(data, activity, plot = TRUE)

```

@@

```{r resample, results = FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- df516b_2
df <- remove_activity_outliers(df)
new_sampling <- 30
new_dgm <- resample_dgm(df, new_sampling)

```

>>>>

```{r}
# Uncomment the below two lines if you use the library for the first time of if
# you want to update the library
# install.packages("devtools")
# devtools::install_github("nasserdr/digiRhythm", dependencies = TRUE)
```
## Example

@@

# The file name with the path
url <- "https://github.com/nasserdr/digiRhythm_sample_datasets/raw/main/516b_2.csv"
download.file(url, destfile = "516b_2.csv")
filename <- file.path(getwd(), "516b_2.csv")

# The columns that we are interested in
colstoread <- c("Date", "Time", "Motion Index", "Steps")

# Reading the activity data from the csv file
data <- import_raw_icetag_data(filename = filename, skipLines = , act.cols.names = colstoread, sampling = 15)

print(head(data))
```

@@

```{r visualize, message=FALSE, warning=FALSE, paged.print=FALSE}
data("df691b_1", package = "digiRhythm")
df <- remove_activity_outliers(df691b_1)
df_act_info(df)
activity <- names(df)[2]
start <- "2020-08-25"
end <- "2020-10-11"
save <- TRUE
outputdir <- "testresults"
outplotname <- "myplot"
width <- 10
device <- "tiff"
height <- 5
actogram(df, activity, start, end,
  save = FALSE,
  outputdir = "testresults", outplotname = "actoplot", width = 10,
  height = 5, device = "tiff"
)
```

@@

```{r dfc_example, results = FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- remove_activity_outliers(df516b_2)
df_act_info(df)
activity <- names(df)[2]
my_dfc <- dfc(df, activity, sampling = 15, show_lsp_plot = FALSE)

# You may want to explore the two list inside my_dfc.
# DFC and SPECTRUM are saved inside my_dfc, each as a list
```

@@

```{r dindex_example, results = FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- remove_activity_outliers(df516b_2)
df_act_info(df)
activity <- names(df)[2]
d_index <- diurnality(data, activity, plot = TRUE)
```

@@

```{r resample, results = FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- df516b_2
df <- remove_activity_outliers(df)
new_sampling <- 30
new_dgm <- resample_dgm(df, new_sampling)
```
